Evaluating Preprocessed TAD Summaries

### 2019-08-25 Scripts/evaluating_preprocessed_tad_summaries.Rmd
edits

res <- c("5kb" ,"10kb", "25kb","50kb", "100kb")
for(i in 1:length(res)){
  domains <- read.table(paste0("Z:/TAD_data_analysis/GM12878/",
                               res[i],
                               "/GM12878_domain_data_",
                               as.integer(gsub("kb", "000", res[i])),
                               ".b.txt"), header=F)
  domains <- domains[,1:3]
  names(domains) <- c("Chromosome","Start","End")

@@

res <- c("5kb" ,"10kb", "25kb","50kb", "100kb")
for(i in 1:length(res)){
  domains <- read.table(paste0("Z:/TAD_data_analysis/K562/",
                               res[i],
                               "/K562_domain_data_",
                               as.integer(gsub("kb", "000", res[i])),
                               ".b.txt"), header=F)
  domains <- domains[,1:3]
  names(domains) <- c("Chromosome","Start","End")

>>>>

res <- c("5kb" ,"10kb", "25kb","50kb", "100kb")
for(i in 1:length(res)){
  domains <- read.table(paste0("Z:/TAD_data_analysis/GM12878/",
                               res[i],
                               "/GM12878_domain_data_",
                               as.integer(gsub("kb", "000", res[i])),
                               ".b.txt"), header=F)
  domains <- domains[,1:3]
  names(domains) <- c("Chromosome","Start","End")
  domains <- domains[-which(domains$Chromosome==9),]

@@

res <- c("5kb" ,"10kb", "25kb","50kb", "100kb")
for(i in 1:length(res)){
  domains <- read.table(paste0("Z:/TAD_data_analysis/K562/",
                               res[i],
                               "/K562_domain_data_",
                               as.integer(gsub("kb", "000", res[i])),
                               ".b.txt"), header=F)
  domains <- domains[,1:3]
  names(domains) <- c("Chromosome","Start","End")
  if("9" %in% names(table(domains$Chromosome))){domains <- domains[-which(domains$Chromosome==9),]}
